Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-03-14 code-tests.tex
Adding section on test suite and test runner.

\red{(Britton)} Description of test suite and test runner.

>>>>

\enzo\ is capable of simulating a large variety of problems types, with
all but a small few requiring only a parameter file as sole input.
The notable exception is the cosmology simulation, which takes as
input initial conditions created by other codes.  These test problems
span a wide range in complexity.  At one end of this spectrum are
simple problems that utilize only a single component of \enzo\ and for
which analytic solutions exist for comparison with the simulation
results.  At the opposite end are problems that exercise a large
portion of \enzo's machinery in concert.  Together, the available
problem types fully cover all of \enzo's functionality.  This enables
them to serve as a vehicle for verifying that the code's behavior
remains stable over time.

\enzo\ uses an automated testing framework that allows a user to run,
with a single command, a set of test problems and compare the results
against results produced by any other version of the code.  Within the
\enzo\ source distribution, the test problem parameter files are stored
in a nested directory structure organized according to the primary
functionality tested, e.g., hydrodynamics, gravity, cooling, etc.
Each parameter file is accompanied by a text file containing various
descriptive keywords, such as the machinery tested, the
dimensionality, and the approximate run time.  A test runner script is
responsible for taking as input from the user a series of keywords
with which to select a subset of all available test problems.  The
test problems are also grouped into three suites: the quick, push, and
full suites, each a superset of the ones named before.  The quick
suite is considered to minimally cover the primary functionality in
\enzo\ and is designed to be run repeatedly during the development
process.  The push suite has slightly increased feature coverage and
is mandated to be run before code changes are accepted into the main
repository.  The full suite consists of all test problems which can be
run with no additional input.  Approximate run times for the quick,
push, and full suite are 15 minutes, 1 hour, and 60 hours,
respectively.

After the test problems are selected by the test runner script, they
are run in succession either by with \enzo\ executable contained within
that distribution or an external executable built from another version
and specified by the user.  This allows for any version of the code to
be tested with an identical set of test problems.  After running the
test problem simulations, the test runner then performs a series of
basic analysis tasks using the \texttt{yt} analysis toolkit
\citep{2011ApJS..192....9T, 2011arXiv1112.4482T}.  The default
analysis performed on all test problems includes calculation of
various statistics, such as extrema; mean; and variance, on the fields
present in the output data.  Custom analysis provided by scripts that
accompany the test problem parameter files is run for special cases,
such as when an analytical solution exists that can be compared
against the simulation data.  After the analysis is performed, the
results are compared against a set of gold standard results which are
maintained on a website and downloaded on the fly by the test runner
script.  Alternately, results from any version of \enzo\ can be stored
locally and compared to any other version of the code.  Below, we
describe some of the key test problems which are used to verify proper 
behavior.
